Kindly Bent to Free Us

### 2020-05-29 kindly/soa.tex
preliminary comparison matrix (w/o callout)

>>>>

\begin{figure}[tp]
  \begin{center}
    \begin{tabular}{l|c|c|c}
      Language& URAL & (Re)borrowing & Impure
      \\\hline
      System F\degree~\citep{DBLP:conf/tldi/MazurakZZ10} & UL & --- & N
      \\
      Alms~\citep{DBLP:conf/popl/TovP11} & UA & --- & Y \\
      Quill~\citep{DBLP:conf/icfp/Morris16} & UL & --- & N \\
      Linear Haskell~\citep{DBLP:journals/pacmpl/BernardyBNJS18} & UL
                     & --- & N \\
      Rust~\citep{rust} & UAL & (Y)Y & Y
      \\\hline
      \lang & UAL & (Y)Y & Y
      \\
    \end{tabular}
  \end{center}
  \caption{Comparison matrix}
  \label{fig:comparison-matrix}
\end{figure}
